---
title: "p8105_hw1_asb2338"
author: "Alexa Burko"
date: "2026-09-20"
output: html_document
---

# Section 0: Libraries
```{r message=F}

library(ggplot2)
library(tidyverse)

```


# Section 1: Load "penguins" dataset
```{r}

data("penguins", package = "palmerpenguins")

```
The names of the variables in this dataset are `r colnames(penguins)`.

The species of penguin included in this dataset are `r unique(penguins$species)` and the islands included in this dataset are `r unique(penguins$island)`.

The dataset has `r nrow(penguins)` observations and `r ncol(penguins)` variables.

The mean flipper length is `r mean(penguins$flipper_length_mm, na.rm = TRUE)`.

# Section 2: Create scatter plot
```{r warning=FALSE}

ggplot(penguins, aes(x=bill_length_mm, y=flipper_length_mm, color=species)) + geom_point()

ggsave(filename="Penguins Scatter Plot.png")

```

# Section 3: Create data frame
```{r}

df = tibble(
  num_var = rnorm(n=10),
  log_var = num_var > 0,
  char_var = c("a", "b", "c", "d", "e", "f", "g", "h", "i", "j"),
  factor_var = factor(c("dog", "cat", "bird", "dog", "dog", "cat", "bird", "bird", "cat", "cat")))

```

The mean num_var is `r mean(df$num_var)`. This worked.

The mean log_var is `r mean(df$log_var)`. This worked.

The mean char_var is `r mean(df$char_var)`. This did not work.

The mean factor_var is `r mean(df$factor_var)`. This did not work.